\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[]{algorithm2e}
\graphicspath{ {./} }
\usepackage{listings}

\lstset{
  columns=fullflexible,
  frame=single,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
}

% Copyright
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\settopmatter{printacmref=false, printccs=false, printfolios=false}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\begin{document}
\title{Paper Recommendation using GraphX} 

\author{Jeremy Chen}
\affiliation{%
  \institution{University of Waterloo}
}
\email{jeremy.chen@uwaterloo.ca}

\author{Junyi Zhang}
\affiliation{%
  \institution{University of Waterloo}
}
\email{j823zhan@uwaterloo.ca}

\author{Yuqing Xie}
\affiliation{%
  \institution{University of Waterloo} }
\email{yuqing.xie@uwaterloo.ca}

% removes footnote with conference information in first column
\renewcommand\footnotetextcopyrightpermission[1]{}
% removes running headers
\pagestyle{plain}


\begin{abstract} \blfootnote{Project source code can be downloaded \href{https://github.com/amyxie361/CS651\_Paper\_recommendation}{\underline{here}}}
Data in graph structure has become popular nowadays.
%
Graph processing framework, therefore, becomes an essential tool to perform scalable computation.
%
GraphX is one of the top choices because of its easiness, scalability, and performance.
%
In this project, we explore GraphX in a deeper way and gain some insights.
%
We achieve this by using GraphX to build an academic paper recommendation system.
%
Without using the trivial way, we implement PageRank, keyword filtering, and pattern finding algorithms in GraphX.
%
We apply them on a citation network to give recommendations of papers, with taking users' interest into account.
%
We have two metrics to evaluate our recommendations: inversion count and ranking distance, and both have given us positive feedback.
%
Through doing this project, we have not only studied GraphX in a practical way but performed data analytics on a citation network.
%
\end{abstract}

\maketitle 

\input{introduction}
\input{related-work}
\input{problem-description}
\input{framework}
\input{algo}
\input{insights}
\input{evaluation}
\input{conclusion}

\bibliographystyle{ACM-Reference-Format}

\bibliography{bibliography}

\end{document}
